Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-06 Paper/paper.tex
Add Figures

\begin{document}
\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–Moriya interactions in antiferromagnetic insulators}

@@

Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$. $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction. $t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping. Where $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). $\sigma^{z}$ is the third Pauli matrix. We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes. In the strong coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$. We can therfore obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second order perturbation techniques in the hopping terms. We can then obtain the effective spin Hamiltonian by using the relations:
\begin{align}
\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \bs{S}_i\cdot\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
\end{align}
Following this procedure we obtain the following effective spin Hamiltonian:

@@

>>>>

\begin{document}
\title{Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators}

@@

Where $\hat{c}_{i \sigma}^\dagger$ ($ \hat{c}_{i \sigma}$) creates (anihilates) an electron at site $i$ in spin state $\sigma$. $\hat{D} = \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$ is the doublon number operator and $\text{U}$ is the on-site interaction. $t_1$, $t_2$ are the hopping amplitudes originating from both kinetic hopping. Where $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). $\sigma^{z}$ is the third Pauli matrix. 
\begin{figure}[t]
\includegraphics[width=0.6\columnwidth]{../Figures/kmh.png}
\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$. $\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
\label{fig1}
\vspace*{-6pt}
\end{figure}
We will assume a half filling system in which the strength of the on-site interaction $\text{U}$ is much larger than the hopping amplitudes. In the strong coupling limit any state with a nonzero number of double occupancies ($d \neq 0$) will have much larger energy than those with $d=0$. We can therfore obtain an effective Hamiltonian acting on the $d=0$ subspace by standard second order perturbation techniques in the hopping terms. We can then obtain the effective spin Hamiltonian by using the relations:
\begin{align}
\hat{c}_{i \sigma}^\dagger \hat{c}_{i \sigma'} &= \delta_{\sigma \sigma'} \frac{1}{2} (n_{i \uparrow} + n_{i \downarrow}) + \bs{S}_i\cdot\bs{\sigma}_{\sigma', \sigma} \label{SpinOperatorInv1}\\ 
\hat{c}_{i \sigma} \hat{c}_{i \sigma'}^\dagger &= \delta_{\sigma \sigma'} \frac{1}{2} (2 - n_{i \uparrow} - n_{i \downarrow}) - \bs{S}_i\cdot\bs{\sigma}_{\sigma, \sigma'} \label{SpinOperatorInv2}
\end{align}
Following this procedure we obtain the following effective spin Hamiltonian:

@@

\begin{figure}[t]
\includegraphics[width=0.6\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
